Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-11 paper.tex
copied submitted version to paper.tex ... and applied my local changes on top via rebase (paper.tex only)

The contributions of this paper are (a) formal re-engineering of the Corona-virus warning app
(b) providing an additional security and privacy analysis with interactive theorem proving
certification of a novel view on the system architecture including actors, locations, and policies,
(c) a formal definition of a security refinement process that allows to improve a system
based on attacks found by the attack tree analysis and (d) an application of the refinement to
improve security of the Corona-virus app specification.

In this paper, we first provide some background in Section \ref{sec:background}:
we give a brief overview of related works
and the protocol of the German app (Section \ref{sec:history}).
We then introduce the Isabelle Infrastructure framework (Section \ref{sec:isainf}).
Next, we present our model (Section \ref{sec:model}) and analysis of privacy and
attacks (Section \ref{sec:ana}). The found attack on the first abstract specification
motivates refinement. The formal definition of refinement for the Isabelle Infrastructure
framework is introduced and illustrated on the Corona-virus warning app (Section \ref{sec:ref})
before drawing some conclusions (Section \ref{sec:concl}).

@@

\section{Background and related work}
\label{sec:background}
\subsection{DP-3T and PEPP-PT}
\label{sec:history}
We are mainly concerned with the architecture and protocols proposed by the
DP-3T (\textit{Decentralized Privacy-Preserving Proximity Tracing}) project \cite{dp3t:github}.
The main reason to focus on this particular family of protocols is the
\textit{Exposure Notification Framework} (ENF), jointly published by Apple and Google \cite{enf:proj}, that adopts
%the main
core principles of the DP-3T proposal. This API is not only used in the German
Corona-virus warning app but has the potential of being widely adopted in future
app developments that might emerge due to the reach of players like Apple and Google.

>>>>

The contributions of this paper are (a) formal re-engineering of the CWA
(b) providing an additional security and privacy analysis with interactive theorem proving
certification of a novel view on the system architecture including actors, locations, and policies,
(c) a formal definition of a security refinement process that allows to improve a system
based on attacks found by the attack tree analysis and (d) an application of the refinement to
improve security of the Corona-virus app specification.

In this paper, we first provide some background in Section \ref{sec:background}:
we give a brief overview of related works
and the protocol of the German app (Section \ref{sec:history}).
We then introduce the Isabelle Infrastructure framework (Section \ref{sec:isainf}).
Next, we present our model (Section \ref{sec:model}) and analysis of privacy and
attacks (Section \ref{sec:ana}). The found attack on the first abstract specification
motivates refinement. The formal definition of refinement for the Isabelle Infrastructure
framework is introduced and illustrated on the CWA (Section \ref{sec:ref})
before drawing some conclusions (Section \ref{sec:concl}).

@@

\section{Background and related work}
\label{sec:background}
\subsection{DP-3T and PEPP-PT}
\label{sec:history}
We are mainly concerned with the architecture and protocols proposed by the
DP-3T (\textit{Decentralized Privacy-Preserving Proximity Tracing}) project \cite{dp3t:github}.
The main reason to focus on this particular family of protocols is the
\textit{Exposure Notification Framework} (ENF), jointly published by Apple and Google \cite{enf:proj}, that adopts
%the main
core principles of the DP-3T proposal. This API is not only used in the German
CWA but has the potential of being widely adopted in future
app developments that might emerge due to the reach of players like Apple and Google.
